---
title: "Democratic Presidential Fundraising as of 01 July 2019"
output: html_notebook
---

## Installation & Setup
```{r setup}
library(dplyr)
library(ggplot2)
library(readr)
```

## Import Data
Source: FEC.gov | Campaign Finance Data | Browse Data | Candidates for President

Filters:

* Election year: 2020
* Time period: 2019-2020
* Political Party: Democratic
```{r data}
# Import data from CSV as tibble (relative path)
data <- read_csv(file = '2019-07-01_dem-POTUS.csv', col_names = TRUE)

# look at the the columns & type of observations contained in each column
str(data)
```


## Clean Data

I'm including only the candidates who were in the first debate, and since Swalwell dropped out I'm replacing him with Montana Governor Steve Bullock.

### Choose columns for analysis

```{r clean}
# select columns you need by name
df <- data[, c("name",
               "cash_on_hand_end_period",
               "receipts",
               "disbursements",
               "debts_owed_by_committee",
               "last_file_date",
               "first_file_date",
               "last_f2_date",
               "address_state",
               "candidate_id",
               "has_raised_funds")]

# look at the data in a new tab
head(df)
```

### Choose candidates for analysis

```{r}
# create a vector of the candidates to be analyzed
# first debate candidates with Bullock

candidates <- c("Bennett", "Biden",
                "Booker", "Bullock",
                "Buttigieg", "Castro",
                "de Blasio", "Delaney",
                "Gabbard", "Gillibrand",
                "Harris", "Inslee",
                "Klobuchar", "Moulton",
                "O'Rourke", "Ryan",
                "Sanders", "Warren",
                "Williamson", "Yang")
```


